---
title: "lab#4"
author: "Tyler Cobian"
date: "1/28/2020"
output: html_document
---
#### Load in the correct packages
###### tidyverse, sf, tmap
```{r setup, include=FALSE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
library(tmap)
```

#### Read in CA Eco-regions data
```{r}
ca_eco<- read_sf(dsn = ".", layer = "ca_eco") %>% 
  select(US_L3NAME) %>% 
  rename(region = US_L3NAME) %>% 
  st_simplify(dTolerance = 100) %>% 
  st_transform(crs = 4326)#as you increase dTolernce it will reduce the number of points that make up a polygon making it more simple
# you can also use the ms_simplify(), geos::gSimplify
plot(ca_eco)
```

#### Read in the CA counties polygons
```{r}
ca_counties<- read_sf(dsn = ".", layer = "california_county_shape_file")
st_crs(ca_counties) = 4326
```

#### Read in CA damn locations and data
```{r}
ca_dams<- read_sf(dsn = ".", layer = "California_Jurisdictional_Dams")
```

#### Make a map of damns in CA overlayed in eco-regions with outlines of CA counties
```{r}
ggplot(ca_counties)+
  geom_sf(color = "black",
          size = 0.1)+
  geom_sf(data = ca_eco,
          aes(fill = region),
          alpha = 0.5,
          color = "NA",
          show.legend = TRUE)+
  geom_sf(data = ca_dams,
          size = 0.5,
          alpha = 0.5)+
  theme_minimal()
```

#### Make the same map as above but only with Santa Barbara eco regions
```{r}
sb<- ca_counties %>% 
  filter(NAME == "Santa Barbara")
# clib the eco region data to only include the SB information with st_intersection()
eco_clip<- st_intersection(ca_eco, sb)
# now we will plot it with ggplot first
ggplot()+
  geom_sf(data = ca_counties, 
          fill = "gray90",
          color = "gray80",
          size = 2)+
  geom_sf(data = eco_clip,
          aes(fill = region),
          color = "white",
          size = 0.4)+
  coord_sf(xlim = c(-121, -119), ylim = c(33.5, 35.5))+
  scale_fill_manual(values = c("darkgreen", "darkorange4", "cyan4"))

```

#### Make an interactive map with tamp
```{r}
sb_clip_tmap<- tm_basemap("CartoDB.DarkMatter")+
  tm_shape(eco_clip)+
  tm_fill("region", palette = c("darkgreen", "darkorange4", "cyan4"), alpha = 0.5)

tmap_mode("view")
sb_clip_tmap
```

#### How to make an sf object from latitude and longitude from and excel sheet
make a mock dataset with tribble()
```{r}
my_example<- tribble(
  ~id, ~lon, ~lat,
  "tiger", -119.4, 34.35,
  "lion", -119.41, 34.39,
  "bear", - 119.43, 34.38
)

# conver this to an sf object
animals_sf<- st_as_sf(my_example, coords = c("lon", "lat"), crs = 4326)
```

Make a map using tmap
```{r}
animal_map<- tm_basemap("CartoDB.Voyager")+
  tm_shape(animals_sf)+
  tm_dots(labels = "id", col = "purple", size = 0.5)
animal_map
```

#### Make a cholorpleth of dam counts
```{r}
intersection<- st_intersection(x = ca_dams, y = ca_counties)

dams_per_county<- intersection %>% 
  group_by(NAME) %>% 
  tally()

ca_tot<- ca_counties %>% 
  st_join(dams_per_county ) %>% 
  select(NAME.x, n) %>% 
  rename(name = NAME.x)

ca_tot_zero<- ca_tot %>% 
  replace_na(list(n = 0))

# make a map with ggplot
ggplot()+
  geom_sf(data = ca_tot_zero,
          aes(fill = n),
          size = 0.2,
          color = "white")+
  scale_fill_continuous(low = "yellow", high = "red")
```

vinettes for sf (google sf package in github)







